\begin{thebibliography}{99}

\bibitem{AptekaaKaliaJvaniseg} A.Aptekarev V.Kaliaguine J.Van Iseghem
The genetic sum's representation for the moments of a system of
Stieltjes functions and its application, Constructive
Approximation, v.16 (2000), pp.487-524.

\bibitem{AptekarevKaliaguine} A.A. Aptekarev, V.A. Kaliaguine,
Complex rational approximation and difference operators \it
Rendiconti del circolo matematico di palermo \rm , serie II,
suppl. 52(1998), pp. 3-21

\bibitem{KaliaguineAA} V.A. Kaliaguine, Hermite-Pade approximants and spectral analysis of noonsymmetric operators
\it Russian Acad. Sci. Sb. Math, \rm  vol. 82(1995), No. 1

\bibitem{KaliaguineAA1} V.A. Kaliaguine, On operators associated with Angelesco systems,
\it East journal on approximations, \rm vol. 1(1995), No. 2

\bibitem{Kaliaguine} V.A. Kaliaguine, The operator moment problem,
vector continued fractions and explicit form ot the Favard theorem
for vector orthogonal polynomials \it J. Comp. Appl. Math. \rm
65(1995) 181-193

\bibitem{KaliaguineRonveaux} V. Kaliaguine, A Ronveaux , On a system of "classical" polynomials of simultaneous orthogonality \it J. Comp. Appl. Math. \rm
67(1996) 207-217

\bibitem{Clenshaw} Clenshaw, C.W., A note on summation of
Chebyshev series, \it Math. Tables Aids Comput. \rm 9, pp 118-120

\bibitem{FischerHJ} H.-J. Fischer, On generating orthogonal polynomials for discrete measures

\bibitem{FischerHJ} H.-J. Fischer, On the condition of orthogonal polynomials via modifie moments,
\it Journal of Analysis and its Applications, \rm vol. 15(1996),
No. 1,1-18

\bibitem{BeckermannBourreau} B. Beckermann, E. Bourreau How to choose modified moments,
\it AMS(MOS): 65D20, 33C45 \rm

\bibitem{GautschiW} Walter Gautschi, Some apllications and numerical methods for orthogonal polynomials,
\it Numerical analysis and mathematical modelling banach center
publications, \rm vol. 24(1990)
\bibitem{GautschiW2} Walter Gautschi, Construction of Gauss-Christoffel quadrature formulas,
\bibitem{GautschiW3} Walter Gautschi, Orthogonal polynomials - constructive theory and applications,
\it Journal of Computational and Applied Mathematics, \rm
vol.12-13(1985) 61-76, North Holland
\bibitem{GautschiW4} Walter Gautschi, Computational aspects of orthogonal polynomials,
\it Orthogonal Polynomials, \rm  1990, pp. 181-216
\bibitem{GautschiW5} Walter Gautschi, On generating orthogonal polynomials,
\it SIAM J. Sci. Stat. Comput., \rm vol. 3, No 3, September (1982)


\bibitem{GoncharAA} А.А. Гончар, О сходимости аппроксимаций Паде
для некоторых классов мероморфных функций \it математический
сборник \rm Т. 97(139), ¦ 4(8), 1975





\bibitem{Nevai} Paul Nevai, Orthogonal polynomials, Mem Amer. Math Soc. 18,No 213



\bibitem{Nikishin} Е.М. Никишин, В.Н. Сорокин, Рациональные аппроксимации и
ортогональность - М.:Наука, 1988

\bibitem{Yurko} V.A. Yurko, On higher-order difference operators \it J. of Diff. Equations
and Appl. \rm 1(1995) 347-352

\bibitem{Henrichi} P.Henrichi Appied and Computational complex Analysis,
John Wiley, 1977, v.2.
\bibitem{jvi} J. Van Iseghem: Vector orthogonal relations. Vector Q.D
 algorithm. J.of Comp. Appl. Math. 19(1987),141-150.

\bibitem{S-VI}V.N.Sorokin, J.Van Iseghem: Algebraic aspects of matrix
orthogonality for vectors polynomials. J.of Appox. Theory
90(1997),97-116.






\bibitem{CabayLabahn} Stan Cabay, George Labahn, A super fast algorithm for multi-dimensional Pade systems,
\it Numerical Algorithms, \rm vol. 2(1992), 201-224
\bibitem{ManticaG} Giorgio Mantica, On computing Jacobi matrices assoiated with recurrent and Mobius iterated function systems,

\bibitem{Izeghem3} J.Van Izeghem, Vector Pade Approximants, proceeding of 11th IMACS Congress 1985 (North Holland, Amsterdam)
\bibitem{Izeghem1} J.Van Izeghem, Vector orthogonal relations. Vector QD-algorithm
\it J. Comp. Appl. Math. \rm 19(1987) 141-150
\bibitem{Izeghem2} J.Van Izeghem, Convergence of the vector QD-algorithm.
Zeroes of vector orthogonal polynomials \it J. Comp. Appl. Math.
\rm 25(1989) 33-46



\bibitem{Backer} Дж. Бейкер, П. Грейвс-Моррис, Аппроксимации Паде - М.:Мир, 1986.


\end{thebibliography}
